### 2024-08-28 paper.tex
kinda basically finished section 7

@@

\begin{corollary}
    The irreducible components of \(\mathcal{Q}_{wr}\) are exactly the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
    Each has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
\end{corollary}
\begin{proof}
    From the foregoing discussion, it is clear that they are indeed the irreducible components.
    To calculate the dimension, we refer to \cref{u_i_rho_irred_and_dim}, which says the dimension is \(\gamma([0, \lambda_1', ..., \lambda_k'])\).
\end{proof}

\par In section 5 we defined the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\) and the principal \(G_{wr}\)-bundle \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\).

@@

\begin{lemma}
    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
    The centralizer of \(J(\lambda)\) in \(\gl_m\) is the subalgebra consisting of matrices 
    \[M = \begin{pmatrix}
        M_{11} & \cdots & M_{1k}\\
        \vdots &        & \vdots\\
        M_{k1} & \cdots & M_{kk}
    \end{pmatrix},\]
    where each \(M_{ij}\) is a \(\lambda_i \times \lambda_j\) matrix, such that each \(M_{ij}\) is lower-left Toeplitz.
\end{lemma}
\begin{proof}
    Let 
    \[M = \begin{pmatrix}
        M_{11} & \cdots & M_{1k}\\
        \vdots &        & \vdots\\
        M_{k1} & \cdots & M_{kk}
    \end{pmatrix}.\]
    We need to show that \(J(\lambda)M = MJ(\lambda)\) if and only if each \(M_{ij}\) is lower-left Toeplitz.
    \par We have 
    \[J(\lambda)M = \begin{pmatrix}
        J_{\lambda_1}M_{11} & \cdots & J_{\lambda_1}M_{1k}\\
        \vdots & & \vdots\\
        J_{\lambda_k}M_{k1} & \cdots & J_{\lambda_k}M_{kk}
    \end{pmatrix}, \textrm{ and } MJ(\lambda) = \begin{pmatrix}
        M_{11} J_{\lambda_1} & \cdots & M_{1k} J_{\lambda_k}\\
        \vdots & & \vdots\\
        M_{k1} J_{\lambda_1} & \cdots & M_{kk} J_{\lambda_k}
    \end{pmatrix}.\]
    So, we have \(J(\lambda)M = MJ(\lambda)\) if and only if \(\forall i,j. \; J_{\lambda_i} M_{ij} = M_{ij} J_{\lambda_j}\).
    Multiplying on the left by \(J_{\lambda_i}\) just shifts each row down by one, and multiplying on the right by \(J_{\lambda_j}\) shifts each column left by one.
    The matrices for which left-shifting gives the same result as down-shifting are exactly the lower-left Toeplitz matrices.
\end{proof}
For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
So, we just have to find 
\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]

>>>>

\begin{lemma}\label{principal_bundle}

@@

\begin{theorem}
    The irreducible components of \(\mathcal{Q}_{wr}\) are exactly the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
    Each has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
\end{theorem}
\begin{proof}
    From the foregoing discussion, it is clear that they are indeed the irreducible components.
    To calculate the dimension, we refer to \cref{u_i_rho_irred_and_dim}, which says the dimension is \(\gamma([0, \lambda_1', ..., \lambda_k'])\).
\end{proof}

\subsection{The varieties \(G_{wr}\) and \(G\)}
Fix \(w,r\).
Recall from section 5 the groups \(G = \{P \in \GL_m : P^{-1}XP = X\}\) and \(G_{wr} = \{A \in G : e_{wr} A = e_{wr}\}\).
\begin{lemma}\label{g_irred_dim}
    \(G\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
\end{lemma}
\begin{proof}
    The closure of \(G\) in \(\gl_m\) is \(\mathfrak{z}_{\gl_m}(X)\).
    \cref{nilpotent_centralizer} says that \(\mathfrak{z}_{\gl_m}(X)\) is isomorphic to \(\mathbb{C}^{\sum_{ij} \min(\lambda_i, \lambda_j)}\).
\end{proof}

\begin{lemma}\label{gwr_irred_dim}
    \(G_{wr}\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
\end{lemma}
\begin{proof}
    The closure of \(G_{wr}\) in \(\gl_m\) is \(V = \{Y \in \mathfrak{z}_{\gl_m}(Y) : e_{wr} Y = e_{wr}\}\).
    Lemma TODO says that \(V\) is isomorphic to \(\mathbb{C}^{\sum_{ij} \min(\lambda_i', \lambda_j')}\).
\end{proof}

\subsection{The components of \(\mathcal{P}_{wr}\)}
Recall from section 5 the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\).
From \cref{principal_bundle} we have the principal \(G_{wr}\)-bundle \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\).
% \par Together, \cref{g_irred_dim} and \cref{gwr_irred_dim} tell us that the irreducible components of \(\mathcal{Q}_{wr} \times G\) are the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G\).

\begin{theorem}\label{pwr_comps}
    The irreducible components of \(\mathcal{P}_{wr}\) are the closures of the images \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\).
    Some irreduble components of \(\mathcal{P}_{wr}\) are double-counted; we have equality iff there's a bijection \(i \leftrightarrow i'\) with \(\rho_i = \rho'_{i'}\) and \(\lambda_i = \lambda_{i'}\).
    When there is no equality, none is in the union of the others.
    Each has dimension blah.
\end{theorem}
\begin{proof}
    TODO: fix statement and proof here.
    Together, \cref{Q_comps} and \cref{g_irred_dim} tell us that \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) is irreducible, and therefore its image is irreducible.
    They are equidimensional, as we will verify in a moment.
    So, to verify that their closures are the irreducible components of \(\mathcal{P}_{wr}\), we need only check that none is contained in the union of the others.
\end{proof}

\subsection{The components of \(\mathcal{P}\)}
\begin{corollary}
    They are just the components of the \(\mathcal{P}_{wr}\)'s.
\end{corollary}

@@

\begin{lemma}\label{nilpotent_centralizer}
    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
    The centralizer of \(J(\lambda)\) in \(\gl_m\) is the subalgebra consisting of matrices 
    \[M = \begin{pmatrix}
        M_{11} & \cdots & M_{1k}\\
        \vdots &        & \vdots\\
        M_{k1} & \cdots & M_{kk}
    \end{pmatrix},\]
    where each \(M_{ij}\) is a \(\lambda_i \times \lambda_j\) matrix, such that each \(M_{ij}\) is lower-left Toeplitz.
\end{lemma}
\begin{proof}
    Let 
    \[M = \begin{pmatrix}
        M_{11} & \cdots & M_{1k}\\
        \vdots &        & \vdots\\
        M_{k1} & \cdots & M_{kk}
    \end{pmatrix}.\]
    We need to show that \(J(\lambda)M = MJ(\lambda)\) if and only if each \(M_{ij}\) is lower-left Toeplitz.
    \par We have 
    \[J(\lambda)M = \begin{pmatrix}
        J_{\lambda_1}M_{11} & \cdots & J_{\lambda_1}M_{1k}\\
        \vdots & & \vdots\\
        J_{\lambda_k}M_{k1} & \cdots & J_{\lambda_k}M_{kk}
    \end{pmatrix}, \textrm{ and } MJ(\lambda) = \begin{pmatrix}
        M_{11} J_{\lambda_1} & \cdots & M_{1k} J_{\lambda_k}\\
        \vdots & & \vdots\\
        M_{k1} J_{\lambda_1} & \cdots & M_{kk} J_{\lambda_k}
    \end{pmatrix}.\]
    So, we have \(J(\lambda)M = MJ(\lambda)\) if and only if \(\forall i,j. \; J_{\lambda_i} M_{ij} = M_{ij} J_{\lambda_j}\).
    Multiplying on the left by \(J_{\lambda_i}\) just shifts each row down by one, and multiplying on the right by \(J_{\lambda_j}\) shifts each column left by one.
    The matrices for which left-shifting gives the same result as down-shifting are exactly the lower-left Toeplitz matrices.
\end{proof}
For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
So, we just have to find 
\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]
